Emulating the CFHTLenS Weak Lensing data: Cosmological Constraints from moments and Minkowski functionals

### 2015-04-16 Paper_minkowski/Submission/reply/reply_referee.tex

\documentclass[11pt]{article}

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{dsfont}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{hyperref}

\addtolength{\hoffset}{-2.5cm}
\addtolength{\textwidth}{4.5cm}
\addtolength{\voffset}{-2cm}
\addtolength{\textheight}{4.5cm}

\begin{document}

\title{Reply to referee's comments, DC11786/Petri}
\author{}
\date{}

\maketitle

\noindent
We thank the referee for the interesting and insightful comments, which we address in this document.

\section*{General comments}

\begin{itemize}
\item \textit{Some cited papers do not match the description}: the desctiptions and references have been updated. The suggested references have been added.
\item \textit{Missing reference to Simon et. al.}: the reference has been added.
\item \textit{Explain the $\dot{\beta}$ notation and the meaning of $\dot{\beta}=0$}: the derivative is taken with respect to the comoving distance $\chi$; an initial condition for the derivative is required to make the Caucky problem well defined. The appropriate explanation has been added to the text.

\item \textit{Definition of $\Theta$ and $\delta_D$}: the definitions of the $\Theta$ and $\delta_D$ functions have been added in the appropriate section
\item \textit{Cubic and quartic moments notations}: we are aware that the definitions of $S_i,K_i$ we adopt are different than the ones provided in [38,39]. Within our statistical framework, these definition mismatches do not matter as they are related to each other via a constant lineat transformation that drops out in the likelihood calculations. The typo $K_4\leftrightarrow K_3$ has been corrected. 
\item \textit{Confusion between $R=1000$ and the 50 independent $N$--body runs in \texttt{CFHTcov}}: the covariance matrices are always estimated from the $R=1000$ lensing field realizations. We believe that the $R$ realizations in the \texttt{CFHTcov} ensemble are more independen than the ones in the \texttt{CFHTemu1} ensemble due to the fact that \texttt{CFHTcov} is bases on 50 independent $N$--body runs. An appropriate explanation has been added to the text. 
\item \textit{Equation (15) (now equation (16)}: here, as throughout the paper, $R=1000$. We added the appropriate clarification
\item \textit{"For this reason, the normalization constant in equation (12) is also model–independent"}: the sentence has been deleted
\item \textit{Accuracy vs relative error}: the wording "accuracy" has been changed to "relative error". The relative error of the PS emulator at low $l$ has been correctly updated to 20\%
\item \textit{Confusion deriving from the $p$ index suppression}: the $p$ index in equation (21) has been reinstated. The sentence "we suppressed the first index of $M(n)$ for notational simplicity" has been deleted

\item \textit{Comment of the large number of components needed in the PCA}: the referee is correct, one of the reasons why large numbers of PCA components are needed might be due to how the PCA is performed. Taking into account the correlation between errors in different bins (i.e. including the covariance matrix due to cosmic variance) will likely reduce the number of components needed. Unfortunately the standard PCA formalism does not allow for such generality. We are currently exploring different extensions to the PCA formalism, whose results will be included in future work

\item \textit{Citation to Heymans et al. (2013) for tomographic lensing constraints}: the citation has been addded

\item \textit{Logic and context of the sentence "We thus attribute this bias to the assumption of linear cosmology-parameter dependence"}: the Fisher matrix formalism is the linear order approximation of our emulator. Using the Fisher matrix in our case would be an oversimplification. A clarifying sentence has been added in the appropriate section

\end{itemize}

\section*{Typos}

\begin{itemize}
\item \textit{"Section III-B first sentence: no 'of'"}: fixed
\item \textit{"eq. (13) 2nd line: the first vector should be transposed"}: fixed
\item \textit{"page 7: thW N = 91 models"}: fixed
\item \textit{"page 8: Odd expression 'In the latter'"}: changed with "in the next section"
\item \textit{"Fig. 7: Labels on y-axes should probably be small sigma"}: $\Sigma_i$ has been replaced with $S_i$

\end{itemize}

\end{document}

### 2015-04-16 Paper_minkowski/Submission/paper.tex
added submission files

%\documentclass[useAMS, usenatbib,usegraphicx,letter]{mn2e}
%\documentclass[11pt]{article}
\documentclass[reprint,aps,prd,superscriptaddress,showkeys,showpacs]{revtex4-1}
\usepackage{epsfig,amsmath,natbib}

@@

\hypersetup{
	colorlinks=false,
	citecolor=green
}
% \usepackage{graphicx}
% \usepackage{epstopdf}
% \usepackage{natbib}

@@

%ZH: changed title a bit
\title{Emulating the CFHTLenS Weak Lensing data:  Cosmological Constraints from Moments and Minkowski Functionals}

@@

%ZH: I reworded the abstract
\begin{abstract}
Weak gravitational lensing is a powerful cosmological probe, with
non--Gaussian features potentially containing the majority of the
information. We examine constraints on the parameter triplet
$(\Omega_m,w,\sigma_8)$ from non-Gaussian features of the weak lensing
convergence field, including a set of moments (up to $4^{\rm th}$
order) and Minkowski Functionals, using publicly available data from
the 154\,deg$^2$ CFHTLenS survey. We utilize a suite of ray--tracing
N-body simulations spanning 91 points in $(\Omega_m,w,\sigma_8)$
parameter space, replicating the galaxy sky positions, redshifts and
shape noise in the CFHTLenS catalogs. We then build an emulator that
interpolates the simulated features as a function of
$(\Omega_m,w,\sigma_8)$, and use it to compute the likelihood function
and parameter constraints. We employ a principal component analysis to
reduce dimensionality and to help stabilize the constraints with
respect to the number of bins used to construct each statistic. Using
the full set of statistics, we find
$\Sigma_8\equiv\sigma_8(\Omega_m/0.27)^{0.55}=0.75\pm0.04$ (68\%
C.L.), in agreement with previous values. We find that constraints on
the $(\Omega_m,\sigma_8)$ doublet from the Minkowski Functionals
suffer a strong bias. However, high-order moments break the
$(\Omega_m,\sigma_8)$ degeneracy and provide a tight constraint on
these parameters with no apparent bias.  The main contribution comes
from quartic moments of gradients.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%% INTRO %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
%

Weak gravitational lensing (hereafter WL) is emerging as a promising
technique to constrain cosmology. Techniques have been developed to
construct cosmic shear fields with shape measurements in large galaxy
catalogues. Although the shear two--point function (2PCF) is the most
widely studied cosmological probe (see, e.g. \citep{CFHTKilbinger}),
alternative statistics have been shown to increase the amount of
cosmological information one can extract from weak lensing
fields. Among these, high--order moments
(\citep{moments1,moments2,moments3,moments4,moments5,moments6}),
three--point functions (\citep{3pcf1,3pcf2}), bispectra
(\citep{bispectrum1,bispectrum2,bispectrum3,bispectrum4}), peak counts
(\citep{peaks1,peaks2,peaks3,peaks4,peaks5,peaks6}) and Minkowski
Functionals (\citep{MinkJan,Petri2013}) have been shown to improve
cosmological constraints in weak lensing analyses.

In this work, we use the publicly available CFHTLenS data, consisting
of a catalog of $\approx$4.2 million galaxies, combined with a suite
of ray-tracing simulations in 91 different cosmological models to
derive constraints on the cosmological parameters $\Omega_m$,
$\sigma_8$ and the dark energy (DE) equation of state $w$.  The
statistics we consider in this work are the Minkowski Functionals
(MFs) and the low--order moments (LM) of the convergence field.
%ZH: I moved this here from the simulation section. Fits better here.
Cosmological parameter inferences from CFHTLenS have been obtained
using the 2PCF~\citep{CFHTKilbinger}, and a number of authors have
investigated the constraining power of CFHTLenS using statistics that
go beyond the usual quadratic ones. Fu et al.~\citep{CFHTFu} used
three--point correlations as an additional probe for cosmology, and
found modest ($10-20\%$) improvements over the 2PCF.  Liu et
al.~\citep{Companion} have found a more significant ($50-60\%$)
tightening of the $\Omega$ and $\sigma_8$ constraints, utilizing the
abundance of WL peaks.
%ZH: We should also cite the CFHT Stripe82 paper by the Chinese, using peak counts, here.
Finally, closest to the present paper, Shirasaki \&
Yoshida~\citep{CFHTMasato} investigated constraints from Minkowski
Functionals, including systematic errors.  Our study represents two
major improvements over previous work.  First, constraints from the
MFs in~ref.~\citep{CFHTMasato} were obtained through the Fisher matrix
formalism, assuming linear dependence on cosmological parameters. Our
study utilizes a suite of simulations sampling the cosmological
parameter space, mapping out the non-linear parameter-dependence of
each descriptor.  Second, we include the LMs as a set of new
descriptors; these yield to the tightest and least biased constraints.

This paper is organized as follows: we first give an overview of the
CFHTLenS catalogs, and summarize the adopted data reduction
techniques. Next, we give a description of our simulation pipeline,
including the ray--tracing algorithm, and the procedure used to sample
the parameter space. We call the statistical weak lensing observables
-- the Power Spectrum, Minkowski Functionals, and Moments --
"descriptors" throughout the paper. We discuss the calculation of the
descriptors, including dimensional reduction using a principal
component analysis, and the statistical inference framework we
used. We then describe our main results, i.e. the cosmological
parameter constraints. To conclude, we then discuss our findings and
comment on possible future extensions of this analysis.

%%%%%%%%%%%%%%%%%%%%%%%%%% DATA AND SIMULATIONS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{CFHTLenS data reduction}
\label{cfhtdatareduction}
%

%ZH: Added lead-in sentence, and moved the last sentence up here:
In this section, we briefly summarize our treatment of the public
CFHTLenS data.  For a more in--depth description of our data reduction
procedure, we refer the reader to \citep{Companion}.

@@

\begin{equation}
\bar{\mathbf{e}}(\pmb{\theta}) = \frac{\sum_{i=1}^{N_s} W(\vert\pmb{\theta}-\pmb{\theta}_i\vert)\mathrm{w}(\pmb{\theta}_i)[\mathbf{e}^{obs}(\pmb{\theta}_i)-c(\pmb{\theta}_i)]}{\sum_{i=1}^{N_s}W(\vert\pmb{\theta}-\pmb{\theta}_i\vert)\mathrm{w}(\pmb{\theta}_i)[1+m(\pmb{\theta})]},
\end{equation} 
\begin{equation}
\label{gausskernel}
W_{\theta_G}(\pmb{\theta}) = \frac{1}{2\pi\theta_G^2}\exp{\left(-\frac{\pmb{\theta}^2}{2\theta_G^2}\right)},
\end{equation}
%
where the smoothing scale $\theta_G$ has been fixed at 1.0\,arcmin
(but varied occasionally to 1.8 and 3.5\,arcmin for specific tests
described below) and $m,c$ refer to the multiplicative and additive
corrections of the galaxies in the catalog.

Using the ellipticity grid $\bar{\mathbf{e}}(\pmb{\theta})$ as an
estimator for the cosmic shear $\gamma^{1,2}(\pmb{\theta})$, we
perform a non--local Kaiser--Squires inversion \citep{KS} to recover
the convergence $\kappa(\pmb{\theta})$ from the $E$--mode of the shear
field,
%
\begin{equation}
\kappa(\mathbf{l}) = \left(\frac{l_1^2-l_2^2}{l_1^2+l_2^2}\right)\gamma^1(\mathbf{l}) + 2\frac{l_1l_2}{l_1^2+l_2^2}\gamma^2(\mathbf{l}).
\end{equation}
%
The simulated $\kappa$ maps we create below are $12~\mathrm{deg}^2$ in
size and have a resolution of $512\times512$ pixels. The CFHTLenS
catalogs contain masked regions (which include the rejected fields and
the regions around bright stars). We first create gridded versions of
the observed $\kappa$ maps matching the size and pixel resolution of
our simulated maps, with each pixel containing the number of galaxies
($n_{gal}$) falling within its window.  
%ZH: I paraphrased the above sentence, because it was ambiguous.  Please check that this is what you meant to say.
We then smooth this galaxy surface density map with the same Gaussian
window function as equation (\ref{gausskernel}) and remove regions
where $n_{gal} < 5 \,\mathrm{arcmin}^{−2}$ (see
\citep{CFHTMasato}). Regions with low galaxy number density can induce
large errors in the cosmological parameter inferences.

@@

We next give a description of our method to sample the parameter space
with a suite of N--body simulations. We wish to investigate the
non--linear dependence of the descriptors (in this work, Minkowski
Functionals and moments of the $\kappa$ field) on the parameter
triplet $\mathbf{p}=(\Omega_m,w,\sigma_8)$, while keeping the other
relevant parameters $(h,\Omega_b,n_s)$ fixed to the values (0.7,
0.046, 0.96). 
%ZH: cite WMAP9 paper here for the parameter choices.
We sampled the $D$--dimensional ($D=3$ in this case) parameter space
using an irregularly spaced grid. The grid was designed with a method
similar to that used to construct an emulator for the matter power
spectrum in the \texttt{Coyote} simulation suite \citep{coyote2}.
Given fixed available computing resources, the irregular grid design
is more efficient than a parameter grid with regular spacings: to
achieve the same average spacing between models in the latter approach
would require a prohibitively large number of simulations.

We limit the parameter sampling to a box whose sides range over
$\Omega_m\in[0.07,1],\,w\in[-3.0,0],\,\sigma_8\in[0.1,1.5]$.  These
are large ranges, with most of the corresponding 3D parameter volume
ruled out by other cosmological experiments. However, our focus in
this work is to quantify the constraints from CFHTLenS alone, which,
by itself has strong parameter degeneracies.
%ZH: Added justification of large ranges above.
We next map this sampling box $\Pi$ into a hypercube of unit side. We
want to construct an irregularly spaced grid consisting of $N$ points
$\mathbf{x}_i\in[0,1]^D$. Let a \textit{design} $\mathcal{D}$ be the
set of this irregularly spaced $N$ points. Our goal is to find an
optimal design, in which the points are spread as uniformly as
possible inside the box. Following ref.~\citep{coyote2}, we choose our
optimal design as the minimum of the cost function

\begin{equation}
\label{costfunction}
\mathcal{C}(\mathcal{D}) = \frac{2D^{1/2}}{N(N-1)}\sum_{i<j}^N\frac{1}{\vert\mathbf{x}_i-\mathbf{x}_j\vert}.
\end{equation} 
%
This problem is mathematically equivalent to the minimization of the
Coulomb potential energy of $N$ unit charges in a unit box, which
corresponds to spreading the charges as evenly as possible.
%, which will make sure that the charges are as evenly spread as possible throughout the confining volume.
Finding the optimal design $\mathcal{D}_m$ that minimizes
(\ref{costfunction}) can be computationally very demanding, and hence
we decided to use a simplified approach. Although approximate, the
following iterative procedure gives satisfactory accuracy for our purposes:

\begin{enumerate}
\item We start from the diagonal design $\mathcal{D}_0$:
$x_i^d\equiv i/(N-1)$ for $d=1...D$.
\item We shuffle the coordinates of the particles in each dimension independently $x_i^d = \mathcal{P}_d\left(\frac{1}{N-1},\frac{2}{N-1},...,1\right)$, where $\mathcal{P}_1,...,\mathcal{P}_D$ are random independent permutations of $(1,2,...,N)$.
\item We pick a random particle pair $(i,j)$ and a random coordinate $d\in\{1,...,D\}$ and swap $x_i^d\leftrightarrow x_j^d$.
\item We compute the new cost function. If the value is less than in the previous step, we keep the exchange, otherwise we revert the coordinate swap.
\item We repeat steps 3 and 4 until the relative cost function change is less than a chosen accuracy parameter $\epsilon$.
\end{enumerate}
%

@@

The goal of this section is to outline our simulation pipeline.  The
fluctuations in the matter density field between a source at redshift
$z$ and an observer located on Earth will cause small deflections in
the trajectories of light rays traveling from the source to the
observer. 
%ZH: I don't think this low-level description is necessary here:
%
%The fluctuations in the matter field are described by the
%gravitational potential
%$\Phi(\mathbf{x},z)=\Phi(\mathbf{x}_\perp,\chi(z))$, where we can
%replace the physical coordinates $\mathrm{x}$ with the comoving
%distance from the observer $\chi$ and two transverse coordinates
%$\mathbf{x}_\perp=\chi\pmb{\beta}$ using the flat sky
%approximation. Here $\pmb{\beta}$ refers to the angular coordinate on
%the sky of a physical point $\mathbf{x}$, as seen from the
%observer. 
We estimate the dark matter gravitational potential running $N$--body
simulations with $N=512^3$ particles, using the public code Gadget2
\citep{Gadget2}. We adopted a comoving box size of $240h^{-1}$Mpc,
corresponding to a mass resolution of $7.4\times10^9h^{-1}M_\odot$.
%ZH: Instead, I added this:
The simulations include dark matter only, and the initial conditions
were generated with \texttt{N-GenIC} at $z=100$, based on the linear
matter power spectrum created with the Einstein-Boltzmann code CAMB
\cite{CAMB}. Data cubes were output at redshift intervals
corresponding to $80h^{-1}$ (comoving) Mpc.

Using a procedure similar to
refs.~\citep{RayTracingJain,RayTracingHartlap}, the equation that
governs the light ray deflections can be written in the form
\begin{equation}
\label{raytrajectory}
\frac{d^2\mathbf{x}(\chi)}{d\chi^2} = -\frac{2}{c^2}\nabla_{\mathbf{x}_\perp}\Phi(\mathbf{x}_\perp(\chi),\chi),
\end{equation}
%
where $\chi$ is the radial comoving distance,
$\mathbf{x}_\perp=\chi\pmb{\beta}$ refers to two transverse
coordinates (with $\pmb{\beta}$ the angular sky coordinates, using the
flat sky approximation)a, $\mathbf{x}(\chi)$ is the trajectory of a
single light ray, and $\Phi$ is the gravitational potential.

Suppose that a light ray reaches the observer at an angular position
$\pmb{\theta}$ on the sky: we want to know where this light ray
originated, knowing it comes from a redshift $z_s$. To answer this
question we need to integrate equation (\ref{raytrajectory}) with the
initial conditions $\pmb{\beta}(0;\pmb{\theta})=\pmb{\theta}$,
$\dot{\pmb{\beta}}(0;\pmb{\theta})=0$ up to a distance
%$w_s=w(z_s)$ to obtain the source angular position $\pmb{\beta}(w_s;\pmb{\theta})$. 
%ZH: any reason to switch from chi to w ?   I switched back.
$\chi_s=\chi(z_s)$ to obtain the source angular position
$\pmb{\beta}(\chi_s;\pmb{\theta})$. We use our proprietary
implementation Inspector Gadget~(see, e.g., \cite{KHM2010}) to solve
for the light ray trajectories based on equation
(\ref{raytrajectory}).

>>>>

\documentclass[reprint,aps,prd,superscriptaddress,showkeys,showpacs]{revtex4-1}
\usepackage{epsfig,amsmath,natbib}

@@

\hypersetup{
	colorlinks=false,
	citecolor=green
}

@@

\title{Emulating the CFHTLenS Weak Lensing data:  Cosmological Constraints from moments and Minkowski functionals}

@@

\begin{abstract}
Weak gravitational lensing is a powerful cosmological probe, with
non--Gaussian features potentially containing the majority of the
information. We examine constraints on the parameter triplet
$(\Omega_m,w,\sigma_8)$ from non-Gaussian features of the weak lensing
convergence field, including a set of moments (up to $4^{\rm th}$
order) and Minkowski functionals, using publicly available data from
the 154\,deg$^2$ CFHTLenS survey. We utilize a suite of ray--tracing
N-body simulations spanning 91 points in $(\Omega_m,w,\sigma_8)$
parameter space, replicating the galaxy sky positions, redshifts and
shape noise in the CFHTLenS catalogs. We then build an emulator that
interpolates the simulated descriptors as a function of
$(\Omega_m,w,\sigma_8)$, and use it to compute the likelihood function
and parameter constraints. We employ a principal component analysis to
reduce dimensionality and to help stabilize the constraints with
respect to the number of bins used to construct each statistic. Using
the full set of statistics, we find
$\Sigma_8\equiv\sigma_8(\Omega_m/0.27)^{0.55}=0.75\pm0.04$ (68\%
C.L.), in agreement with previous values. We find that constraints on
the $(\Omega_m,\sigma_8)$ doublet from the Minkowski functionals
suffer a strong bias. However, high-order moments break the
$(\Omega_m,\sigma_8)$ degeneracy and provide a tight constraint on
these parameters with no apparent bias.  The main contribution comes
from quartic moments of derivatives.
\end{abstract}

@@

\section{Introduction}

Weak gravitational lensing (hereafter WL) is emerging as a promising
technique to constrain cosmology. Techniques have been developed to
construct cosmic shear fields with shape measurements in large galaxy
catalogues. Although the shear two--point function (2PCF) is the most
widely studied cosmological probe (see, e.g. \citep{CFHTKilbinger}),
alternative statistics have been shown to increase the amount of
cosmological information one can extract from weak lensing
fields. Among these, high--order moments
(\citep{moments1,moments2,moments3,moments4,moments5}),
three--point functions (\citep{3pcf1,3pcf2,3pcf3}), bispectra
(\citep{bispectrum1,bispectrum2,bispectrum3,bispectrum4}), peak counts
(\citep{peaks1,peaks2,peaks3,peaks4,peaks5,peaks6,peaks7,peaks8}) and Minkowski
Functionals (\citep{MinkJan,Petri2013}) have been shown to improve
cosmological constraints in weak lensing analyses.

In this work, we use the publicly available CFHTLenS data, consisting
of a catalog of $\approx$4.2 million galaxies, combined with a suite
of ray-tracing simulations in 91 different cosmological models to
derive constraints on the cosmological parameters $\Omega_m$,
$\sigma_8$ and the dark energy (DE) equation of state $w$.  The
statistics we consider in this work are the Minkowski functionals
(MFs) and the low--order moments (LM) of the convergence field.
Cosmological parameter inferences from CFHTLenS have been obtained
using the 2PCF~\citep{CFHTKilbinger}, and a number of authors have
investigated the constraining power of CFHTLenS using statistics that
go beyond the usual quadratic ones. Fu et al.~\citep{CFHTFu} used
three--point correlations as an additional probe for cosmology, and
found modest ($10-20\%$) improvements over the 2PCF. \textbf{These results rely on the third order statistics systematic tests performed by Simon et al. \citep{CFHTSimon}}.

Liu et al.~\citep{Companion} have found a more significant ($50-60\%$)
tightening of the $\Omega$ and $\sigma_8$ constraints, utilizing the
abundance of WL peaks. Cosmological constraints using WL peaks in CFHTLenS Stripe82 data
have also been investigated by Liu et. al.~\citep{Stripe82}. 
Finally, closest to the present paper, Shirasaki \&
Yoshida~\citep{CFHTMasato} investigated constraints from Minkowski
Functionals, including systematic errors.  Our study represents two
major improvements over previous work.  First, constraints from the
MFs in~ref.~\citep{CFHTMasato} were obtained through the Fisher matrix
formalism, assuming linear dependence on cosmological parameters. Our
study utilizes a suite of simulations sampling the cosmological
parameter space, mapping out the non-linear parameter-dependence of
each descriptor.  Second, we include the LMs as a set of new
descriptors; these yield the tightest and least biased constraints.

This paper is organized as follows: we first give an overview of the
CFHTLenS catalogs, and summarize the adopted data reduction
techniques. Next, we give a description of our simulation pipeline,
including the ray--tracing algorithm, and the procedure used to sample
the parameter space. We call the statistical weak lensing observables
-- the power spectrum, Minkowski functionals, and moments --
"descriptors" throughout the paper. We discuss the calculation of the
descriptors, including dimensional reduction using a principal
component analysis, and the statistical inference framework we
used. We then describe our main results, i.e. the cosmological
parameter constraints. To conclude, we then discuss our findings and
comment on possible future extensions of this analysis.

@@

\subsection{CFHTLenS data reduction}
\label{cfhtdatareduction}

In this section, we briefly summarize our treatment of the public
CFHTLenS data.  For a more in--depth description of our data reduction
procedure, we refer the reader to \citep{Companion}.

@@

\begin{equation}
\bar{\mathbf{e}}(\pmb{\theta}) = \frac{\sum_{i=1}^{N_s} W(\vert\pmb{\theta}-\pmb{\theta}_i\vert)\mathrm{w}(\pmb{\theta}_i)[\mathbf{e}^{obs}(\pmb{\theta}_i)-c(\pmb{\theta}_i)]}{\sum_{i=1}^{N_s}W(\vert\pmb{\theta}-\pmb{\theta}_i\vert)\mathrm{w}(\pmb{\theta}_i)[1+m(\pmb{\theta})]},
\end{equation} 
\begin{equation}
\label{gausskernel}
W_{\theta_G}(\pmb{\theta}) = \frac{1}{2\pi\theta_G^2}\exp{\left(-\frac{\pmb{\theta}^2}{2\theta_G^2}\right)},
\end{equation}
where the smoothing scale $\theta_G$ has been fixed at 1.0\,arcmin
(but varied occasionally to 1.8 and 3.5\,arcmin for specific tests
described below) and $m,c$ refer to the multiplicative and additive
corrections of the galaxies in the catalog.

Using the ellipticity grid $\bar{\mathbf{e}}(\pmb{\theta})$ as an
estimator for the cosmic shear $\gamma^{1,2}(\pmb{\theta})$, we
perform a non--local Kaiser--Squires inversion \citep{KS} to recover
the convergence $\kappa(\pmb{\theta})$ from the $E$--mode of the shear
field,
\begin{equation}
\kappa(\mathbf{l}) = \left(\frac{l_1^2-l_2^2}{l_1^2+l_2^2}\right)\gamma^1(\mathbf{l}) + 2\frac{l_1l_2}{l_1^2+l_2^2}\gamma^2(\mathbf{l}).
\end{equation}
The simulated $\kappa$ maps we create below are $12~\mathrm{deg}^2$ in
size and have a resolution of $512\times512$ pixels. The CFHTLenS
catalogs contain masked regions (which include the rejected fields and
the regions around bright stars). We first create gridded versions of
the observed $\kappa$ maps matching the size and pixel resolution of
our simulated maps, with each pixel containing the number of galaxies
($n_{gal}$) falling within its window.  
We then smooth this galaxy surface density map with the same Gaussian
window function as equation (\ref{gausskernel}) and remove regions
where $n_{gal} < 5 \,\mathrm{arcmin}^{−2}$ (see
\citep{CFHTMasato}). Regions with low galaxy number density can induce
large errors in the cosmological parameter inferences.

@@

We next give a description of our method to sample the parameter space
with a suite of N--body simulations. We wish to investigate the
non--linear dependence of the descriptors (in this work, Minkowski
Functionals and moments of the $\kappa$ field) on the parameter
triplet $\mathbf{p}=(\Omega_m,w,\sigma_8)$, while keeping the other
relevant parameters $(h,\Omega_b,n_s)$ fixed to the values (0.7,
0.046, 0.96) (see \citep{WMAP9}).
We sampled the $D$--dimensional ($D=3$ in this case) parameter space
using an irregularly spaced grid. The grid was designed with a method
similar to that used to construct an emulator for the matter power
spectrum in the \texttt{Coyote} simulation suite \citep{coyote2}.
Given fixed available computing resources, the irregular grid design
is more efficient than a parameter grid with regular spacings: to
achieve the same average spacing between models in the latter approach
would require a prohibitively large number of simulations.

We limit the parameter sampling to a box whose sides range over
$\Omega_m\in[0.07,1],\,w\in[-3.0,0],\,\sigma_8\in[0.1,1.5]$.  These
are large ranges, with most of the corresponding 3D parameter volume
ruled out by other cosmological experiments. However, our focus in
this work is to quantify the constraints from CFHTLenS alone, which,
by itself has strong parameter degeneracies.
We next map this sampling box $\Pi$ into a hypercube of unit side. We
want to construct an irregularly spaced grid consisting of $N$ points
$\mathbf{x}_i\in[0,1]^D$. Let a \textit{design} $\mathcal{D}$ be the
set of this irregularly spaced $N$ points. Our goal is to find an
optimal design, in which the points are spread as uniformly as
possible inside the box. Following ref.~\citep{coyote2}, we choose our
optimal design as the minimum of the cost function

\begin{equation}
\label{costfunction}
\mathcal{C}(\mathcal{D}) = \frac{2D^{1/2}}{N(N-1)}\sum_{i<j}^N\frac{1}{\vert\mathbf{x}_i-\mathbf{x}_j\vert}.
\end{equation} 
This problem is mathematically equivalent to the minimization of the
Coulomb potential energy of $N$ unit charges in a unit box, which
corresponds to spreading the charges as evenly as possible.
Finding the optimal design $\mathcal{D}_m$ that minimizes
(\ref{costfunction}) can be computationally very demanding, and hence
we decided to use a simplified approach. Although approximate, the
following iterative procedure gives satisfactory accuracy for our purposes:

\begin{enumerate}
\item We start from the diagonal design $\mathcal{D}_0$:
$x_i^d\equiv i/(N-1)$ for $d=1...D$.
\item We shuffle the coordinates of the particles in each dimension independently $x_i^d = \mathcal{P}_d\left(\frac{1}{N-1},\frac{2}{N-1},...,1\right)$, where $\mathcal{P}_1,...,\mathcal{P}_D$ are random independent permutations of $(1,2,...,N)$.
\item We pick a random particle pair $(i,j)$ and a random coordinate $d\in\{1,...,D\}$ and swap $x_i^d\leftrightarrow x_j^d$.
\item We compute the new cost function. If the value is less than in the previous step, we keep the exchange, otherwise we revert the coordinate swap.
\item We repeat steps 3 and 4 until the relative cost function change is less than a chosen accuracy parameter $\epsilon$.
\end{enumerate}

@@

The goal of this section is to outline our simulation pipeline.  The
fluctuations in the matter density field between a source at redshift
$z$ and an observer located on Earth will cause small deflections in
the trajectories of light rays traveling from the source to the
observer. 
We estimate the dark matter gravitational potential running $N$--body
simulations with $N=512^3$ particles, using the public code Gadget2
\citep{Gadget2}. We adopted a comoving box size of $240h^{-1}$Mpc,
corresponding to a mass resolution of $7.4\times10^9h^{-1}M_\odot$.
The simulations include dark matter only, and the initial conditions
were generated with \texttt{N-GenIC} at $z=100$, based on the linear
matter power spectrum created with the Einstein-Boltzmann code CAMB
\cite{CAMB}. Data cubes were output at redshift intervals
corresponding to $80h^{-1}$ (comoving) Mpc.

Using a procedure similar to
refs.~\citep{RayTracingJain,RayTracingHartlap}, the equation that
governs the light ray deflections can be written in the form
\begin{equation}
\label{raytrajectory}
\frac{d^2\mathbf{x}(\chi)}{d\chi^2} = -\frac{2}{c^2}\nabla_{\mathbf{x}_\perp}\Phi(\mathbf{x}_\perp(\chi),\chi),
\end{equation}
where $\chi$ is the radial comoving distance,
$\mathbf{x}_\perp=\chi\pmb{\beta}$ refers to two transverse
coordinates (with $\pmb{\beta}$ the angular sky coordinates, using the
flat sky approximation)a, $\mathbf{x}(\chi)$ is the trajectory of a
single light ray, and $\Phi$ is the gravitational potential.

Suppose that a light ray reaches the observer at an angular position
$\pmb{\theta}$ on the sky: we want to know where this light ray
originated, knowing it comes from a redshift $z_s$. To answer this
question we need to integrate equation (\ref{raytrajectory}) with the
initial condition $\pmb{\beta}(0;\pmb{\theta})=\pmb{\theta}$ up to a distance
$\chi_s=\chi(z_s)$ to obtain the source angular position
$\pmb{\beta}(\chi_s;\pmb{\theta})$. \textbf{Since light rays travel undeflected from the observer to the first lens plane, the derivative initial condition in the Cauchy problem (\ref{raytrajectory}) reads $\dot{\pmb{\beta}}(0;\pmb{\theta})=0$. We indicate the derivative of $\pmb{\beta}$ with respect to $\chi$ as $\dot{\pmb{\beta}}$.} 
%
We use our proprietary implementation Inspector Gadget~(see, e.g., \cite{KHM2010}) to solve
for the light ray trajectories based \textbf{on a discretized version of equation (\ref{raytrajectory}) that is based on the multi--lens--plane algorithm (see \citep{RayTracingHartlap} for example).
Applying random periodical shifts and rotations to the $N$--body simulation data cubes, we generate $R=1000$ pseudo--independent realizations of the lens plane system used to solve (\ref{raytrajectory}).} 
%
Once we obtain the light ray trajectories, we infer the relevant weak
lensing quantities by taking angular derivatives of the ray
deflections $A(\chi_s;\pmb{\theta}) = \partial
\pmb{\beta}(\chi_s;\pmb{\theta})/\partial\pmb{\theta}$ and performing
the usual spin decomposition to infer the convergence $\kappa$ and the
shear components $(\gamma^1,\gamma^2)$,
\begin{equation}
A(\chi_s;\pmb{\theta}) = (1-\kappa(\chi_s;\pmb{\theta}))\pmb{I} - \gamma^1(\chi_s;\pmb{\theta})\sigma^3 - \gamma^2(\chi_s;\pmb{\theta})\sigma^1
\end{equation}  
where $\pmb{I}$ is the $2\times2$ identity and $\sigma^{1,3}$ are the
first and third Pauli matrices. \textbf{We perform this procedure for each of the $R$ realizations of the lens planes and we obtain $R$ pseudo--independent realizations of the $\pmb{\gamma}$ weak lensing field.} We use these different random realizations to estimate the means \textbf{(from the \texttt{CFHTemu1} simulations)} and covariance matrices \textbf{(from the \texttt{CFHTcov} simulations)} of our descriptors. \textbf{Since the random box rotations and translations that make up the \texttt{CFHTcov} simulations are based on 50 independent $N$--body runs, we believe the covariance matrices measured from this set to be more accurate than the ones measured from the \texttt{CFHTemu1} set.}

The convergence $\kappa$ is related to
the magnification, while the two components of the complex shear
$\pmb{\gamma}=\gamma^1 + i\gamma^2$ are related to the apparent
ellipticity of the source. Given a source with intrinsic complex
ellipticity $\mathbf{e}_s=e^1_s + ie^2_s$, its observed ellipticity
will be modified to
\begin{equation}
\mathbf{e} = 
\begin{cases}
\frac{\mathbf{e}_s+\mathbf{g}}{1+\mathbf{g}^*\mathbf{e}_s} \,\,\,\,\,\,\,\, \vert \mathbf{g}\vert \leq 1 \\ \\
\frac{1+\mathbf{ge}_s^*}{\mathbf{e}_s^* + \mathbf{g}^*} \,\,\,\,\,\,\,\, \vert \mathbf{g}\vert > 1
\end{cases}
\end{equation}
where $\mathbf{g} \equiv \pmb{\gamma}/(1-\kappa)$ is the reduced shear.
